\thesistitle

### 2019-07-25 sections/introduction.tex
Research method: attempt numero dos

>>>>

\subsection{Research method}
We perform an \textbf{exploratory} study to look into the opportunities to automatically refactor code clones. To do this, we combine knowledge from literature with our own experience to develop definitions for refactorable clones. We also develop a tool to detect, analyze and refactor such clones. Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open source software. In these experiments we control several variables to see their impact on the results. During this process we explore concepts and develop understanding, because of which decisions in the study design are based upon the results of the experiments.
